Notes on Wide Gap

### 2016-03-31 paper/wide_gap_notes.tex
all terms accounted for .. please check equations 28 - 31
wide gap nonlinear vector

The $\rhat$ terms will have $\partial_z$ applied to them, which will destroy the $3\Omega(r)^2 r \rhat$ term and so the righthand side of the $\Psi$ equation will ultimately gain only the term $2 \Omega(r) \partial_z u_\phi \rhat$.

@@

\begin{multline}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi - \partial_z\left(u_\phi \Omega(r) \right)\\
= \frac{2}{\beta} J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{\beta} \frac{2}{r}B_\phi \partial_z B_\phi + 2 \Omega(r) \partial_z u_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right] + \frac{2}{\beta} \frac{1}{r}B_0 \partial_z \left(\nabla^2 A - \frac{2}{r} \partial_r A\right) 
\end{multline}

@@

\begin{equation}
  \label{eq:uy_perturbed}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} + \partial_z\Psi\left( \frac{2}{r}\Omega(r) + \partial_r \Omega(r) \right) = \frac{2}{\beta} \frac{J(A, B_\phi)}{r} + \frac{2}{\beta} \frac{B_\phi \partial_z A}{r^2} + \frac{1}{\reye} \left( \nabla^2 \uphi - \frac{\uphi}{r}\right) + \frac{2}{\beta} B_0 \partial_z B_\phi
\end{equation}

@@

\appendix

>>>>

The $\rhat$ terms will have $\partial_z$ applied to them, which will destroy the $3\Omega(r)^2 r \rhat$ term and so the righthand side of the $\Psi$ equation will ultimately gain only the term $2 \Omega(r) \partial_z u_\phi \rhat$. The $\phihat$ equation gains the term $-\frac{2}{r} \Omega(r) \partial_z \Psi$ on the righthand side.

@@

\begin{multline}
\label{eq:Psi_perturbed}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi - \partial_z\left(u_\phi \Omega(r) \right)\\
= \frac{2}{\beta} J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{\beta} \frac{2}{r}B_\phi \partial_z B_\phi + 2 \Omega(r) \partial_z u_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right] + \frac{2}{\beta} \frac{1}{r}B_0 \partial_z \left(\nabla^2 A - \frac{2}{r} \partial_r A\right) 
\end{multline}

@@

\begin{multline}
  \label{eq:uy_perturbed}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} + \partial_z\Psi\left( \frac{2}{r}\Omega(r) + \partial_r \Omega(r) \right) = \\
\frac{2}{\beta} \frac{J(A, B_\phi)}{r} + \frac{2}{\beta} \frac{B_\phi \partial_z A}{r^2} + \frac{1}{\reye} \left( \nabla^2 \uphi - \frac{\uphi}{r}\right) + \frac{2}{\beta} B_0 \partial_z B_\phi -\frac{2}{r} \Omega(r) \partial_z \Psi
\end{multline}

@@

\section{Matrix Formulation}

This is all pending a rigorous check of Equations \ref{eq:Psi_perturbed} - \ref{eq:By_perturbed}, which Jeff is working on, but I'll start putting this into a matrix construction.

First, the nonlinear vector, on the lefthand side of the equation, is

\beq
\mathbf{N} = \left[\begin{matrix}
J\left(\Psi, \frac{1}{r^2} \left(\nabla^2 \Psi - \frac{2}{r}\partial_r \Psi \right) \right) - \frac{2}{\beta} J \left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_r A\right)\right) - \frac{2}{r} u_\phi \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r} B_\phi \partial_z B_\phi \\
\frac{1}{r} J \left(\Psi, u_\phi\right) - \frac{1}{r} \frac{2}{\beta} J \left(A, B_\phi\right) + \frac{1}{r^2} u_\phi \partial_z \Psi - \frac{2}{\beta} \frac{1}{r^2} B_\phi \partial_z A \\
-\frac{1}{r} J \left(A, \Psi\right)\\
-\frac{1}{r} J \left(A, u_\phi\right) - \frac{1}{r} J \left(B_\phi, \Psi\right) - \frac{1}{r^2} B_\phi \partial_z \Psi + \frac{1}{r^2} u_\phi \partial_z A
\end{matrix}\right] 
\eeq

Note that these differ from the thin-gap nonlinear terms not only because of the curvature terms in the Jacobians, but also because of the additional advective terms in all but the $\mathbf{A}$ equation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                              APPENDIX                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
